Fictitious Play in Network Aggregative Games

### 2021-04-26 Documents/FP in NAGs/FPNAG.tex
Resolved Conflicts

		\subsection{Related Work}
					Main articles: 
					\begin{enumerate}
						\item Ewerhart (FP in Networks). Main difference is in the model we consider - i.e. agents only track the aggregate strategy rather than strategies of all neighbours. Further, our analysis shows that in non-simple networks, FP still converges to a fixed point, although not an NE.
						\item Grammatico (NE seeking in NA games). Main difference is that we look at the case where the payoffs are bilinear (since in matrix form), so that we need to consider best response correspondences rather than assuming a unique minimiser.
						\item Perrin (FP in Mean Field Games). Main difference is that we assume an underlying communication network rather than assuming that the players play against the entire population (which is a special case of our analysis, in which you assume that all players are connected to each other).
						\item Sela (FP in one-against-all networks) Similarly, this paper doesn't assume an underlying communication network or any form of weighted communication between the agents.
					\end{enumerate}

		\section{Preliminaries}
	\subsection{Network Aggregative Games}
	\label{sec::NAG}

	The model we consider is that there is a set $\agentset = {1,
         \ldots , N}$ of agents who are connected through an underlying
        interaction graph. This graph is given by the tuple
        $(\agentset, (\edgeset, \weightset))$ in which $\edgeset$ is
        the set of all pairs $(\mu, \nu) \in \agentset \times
        \agentset$ such that agent $\mu$ and agent $\nu$ are
        connected. Formally,

@@

        We can construct the \fb{unit-simplex ?} on the action
        set as $\Delta_\mu := \{x \in \mathbb{R}^n \, : \, \sum_i
        \xmuaction{i} = 1\}$ where $\xmuaction{i}$ is the probability
        with which agent $\mu$ plays the action $i$. As such we
        refer to $\xmu$ as the \emph{state} of agent $\mu$ (this is
        often referred to as $\mu$'s mixed strategy). Also associated
        with each agent is a utility function $u^\mu(\xmu, \xnotmu)$
        in which we use the standard notation $-\mu$ to refer to all
        agents other than $\mu$. Notice that this requires that each
        agent plays the same strategy against all of their neighbours.

@@

	\begin{definition}[Network Aggregative Game]
		A Network Aggregative game is defined as the tuple $\Gamma =
        (\agentset, (\edgeset, \weightset), (\actionset{\mu},
        \utility{\mu})_{\mu \in \mathcal{N}})$, where $\agentset$, $\edgeset$, $\weightset$ are as
        defined in the Interaction graph. $\actionset{\mu}$ and $\utility{\mu}$ refer to the set of
        actions and the utility function of agent $\mu$ respectively..
	\end{definition}

@@

	Fictitious Play requires that, at the current time, each agent
        considers the average behaviour of their opponent in the past
        and play a best response to that strategy. This is best
        illustrated in the two-player setting. Consider the two player
        normal form game $\Gamma_2 = (\{ 1, 2\}, ((S^1, A), (S^2,
        B)))$ so that $A$ and $B$ are the payoff matrices of agent $1$
        and $2$ respectively. As a remark, note that we can write the
        two player normal form game as an NA game simply by requiring
        that $\edgeset = \{(1, 2), (2, 1)\}$ and $\weightset$ is a 2x2
        matrix with zeros on its leading diagonal and ones on the off
        diagonal. We write the time-average of both agents' strategies
        as
%
	\begin{align}
		\alpha^i = \frac{1}{t} \int_0^T x^i(t) \, dt & \text{ for $i \in \{1, 2\}$}
%		\alpha^2 = \frac{1}{t} \int_0^T x^2(t) \, dt \\
	\end{align}
        \fb{why using an integral rather than a simple summation?}

@@

	Using this, we follow in the footsteps of Ewerhart \cite{} and Harris \cite{} to define
	Fictitious Play in continuous time.
%
	\begin{definition}[Continuous Time Fictitious Play (CTFP)]
		A CTFP is defined as a measurable map $m$ with components $m_i$ such that for all $i$ and
		all $t \geq 1$, $m_i: [0, \infty) \rightarrow \Delta_i$ satisfies $m_i(t) \in
		BR_i(\alpha_{\sigma_i})$ for almost all $t \geq 1$.
	\end{definition}

@@

	\subsection{Assumption}

>>>>

	\subsection{Network Aggregative Games}
	\label{sec::NAG}

	The model we consider is that there is a set $\agentset = {1,
         \ldots , N}$ of agents who are connected through an underlying
        interaction graph. This graph is given by the tuple
        $(\agentset, (\edgeset, \weightset))$ in which $\edgeset$ is
        the set of all pairs $(\mu, \nu) \in \agentset \times \agentset$
        connected. Formally,

@@

        We can construct the \fb{unit-simplex ?} on the action
        set as $\Delta_\mu := \{\xmu \in \mathbb{R}^n \, : \, \sum_i
        \xmuaction{i} = 1\}$ where $\xmuaction{i}$ is the probability
        with which agent $\mu$ plays the action $i$. As such we
        refer to $\xmu$ as the \emph{state} of agent $\mu$ (this is
        often referred to as $\mu$'s mixed strategy). Also associated
        with each agent is a utility function $u^\mu(\xmu, \xnotmu)$
        in which we use the standard notation $-\mu$ to refer to all
        agents other than $\mu$. Notice that this requires that each
        agent plays the same strategy against all of their neighbours.

@@

	\begin{definition}[Network Aggregative Game]
		A Network Aggregative game is defined as the tuple $\Gamma =
        (I, (\actionset{\mu},
        \utility{\mu})_{\mu \in \mathcal{N}})$, where $I$ is the interaction graph, $\actionset{\mu}$ and $\utility{\mu}$ refer to the set of
        actions and the utility function of agent $\mu$ respectively.
	\end{definition}

@@

	Fictitious Play requires that, at the current time, each agent
        considers the average behaviour of their opponent in the past
        and play a best response to that strategy. This is best
        illustrated in the two-player setting. Consider the two player
        normal form game $\Gamma_2 = (\{ 1, 2\}, ((S^1, A), (S^2,
        B)))$ so that $A$ and $B$ are the payoff matrices of agent $1$
        and $2$ respectively. As a remark, note that we can write the
        two player normal form game as an NA game simply by requiring
        that $\edgeset = \{(1, 2), (2, 1)\}$ and $\weightset$ is a 2x2
        matrix with zeros on its leading diagonal and ones on the off
        diagonal. We write the time-average of both agents' strategies
        as
%
	\begin{align}
		\alpha^\mu = \frac{1}{t} \int_0^T \xmu(t) \, dt & \text{ for $\mu \in \{1, 2\}$}
%		\alpha^2 = \frac{1}{t} \int_0^T x^2(t) \, dt \\
	\end{align}
        \fb{why using an integral rather than a simple summation?}

@@

	Using this, we follow in the footsteps of Ewerhart \cite{} and Harris \cite{} to define
	Fictitious Play in continuous time.
%
	\begin{definition}[Continuous Time Fictitious Play (CTFP)]
		A CTFP is defined as a measurable map $m$ with components $m^\mu$ such that for all $\mu$
		and all $t \geq 1$, $m^\mu: [0, \infty) \rightarrow \Delta_\mu$ satisfies $m^\mu(t) \in
		BR^\mu(\alpha_{\sigma}^\mu)$ for almost all $t \geq 1$.
	\end{definition}

@@

	\subsection{Assumptions}
